---
title: "HW5"
author: "Danny Nguyen"
date: "2023-11-10"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(readr)
library(rvest)
library(dplyr)
library(broom)
```

### Import Data
```{r}
homicide <- read_csv("homicide-data.csv")
```
This dataframe has `r nrow(homicide)` rows and `r ncol(homicide)` columns of criminal homicides across 50 major U.S. cities over a decade, detailing locations, arrest rates, and victim demographics, such as `reported_date`, `victim_race`, `victim_gender`, `disposition` etc. 

```{r}
homicide <- homicide %>% 
  mutate(city_state = paste(city, state, sep =", ")) 

unresolved = homicide %>% 
  group_by(city_state) %>% 
  summarize( 
    total_homicide = n(),
    unsolved = sum(disposition %in% c("Closed without arrest", "Open/No arrest"))) %>%
  filter(city_state != "Tulsa, AL")

unresolved
```

### Baltimore Unresolved Homicides
```{r}
baltimore <- unresolved %>% 
  filter(city_state == "Baltimore, MD")

baltimore_test <- prop.test(
  x= baltimore %>% pull(unsolved),
  n = baltimore %>%pull(total_homicide))%>% 
  broom::tidy()

baltimore_test
```
The estimated proportion of homicides in Baltimore, MD is 64.6% and its 95%CI interval is (62.8%, 66.3%).

### Plot: The Estimates and CIs for Each City
```{r}
prop_cities = unresolved %>% 
  mutate(
    test = map2(.x = unsolved, .y = total_homicide, ~prop.test(x = .x, n = .y)),
    test = map(test,broom::tidy))%>%
  unnest() %>%
  select(city_state, estimate, conf.low, conf.high)%>%
  arrange(desc(estimate))

prop_cities %>%
  ggplot(aes(x=reorder(city_state, estimate), y= estimate)) + 
  geom_point() + 
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) +
   labs(title = "Estimates and 95%CIs for each city",x = "City", y = "Proportion of unsolved homicides") +   
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
```


